Chapter 4

### 2021-08-05 thesis_chapter_4.Rmd
updated chapter 4 heatmaps

---
title: "Chapter 4"
author: "Ross Coppin"
date: "11/12/2020"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

@@

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

@@

@@

summer_heatmap <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_hex(data = total_summer, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 100000)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_summer_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("1") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

autumn_heatmap <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_hex(data = total_autumn, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 110000)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_autumn_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("1") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

autumn_heatmap <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_hex(data = total_winter, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 110000)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_winter_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("1") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12)) 
# Spring

autumn_heatmap <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_hex(data = total_spring, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 110000)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_spring_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("1") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12)) 
```

>>>>

---
title: "Chapter 4"
author: "Ross Coppin"
date: "11/12/2020"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

@@

```{r data wrangle, message=FALSE, warning=FALSE, include=FALSE}

@@

total_summer_surface <- total_summer %>% 
filter(KelpDepth == 0)
total_summer_sink <- total_summer %>% 
filter(KelpDepth > 0)
total_autumn_surface <- total_autumn %>% 
filter(KelpDepth == 0)
total_autumn_sink <- total_autumn %>% 
filter(KelpDepth > 0)
total_winter_surface <- total_winter %>% 
filter(KelpDepth == 0)
total_winter_sink <- total_winter %>% 
filter(KelpDepth > 0)
total_spring_surface <- total_spring %>% 
filter(KelpDepth == 0)
total_spring_sink <- total_spring %>% 
filter(KelpDepth > 0)

@@

# summer
summer_heatmap_surface <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_hex(data = total_summer_surface, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 100000)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_summer_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("Surface") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

summer_heatmap_sink <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_hex(data = total_summer_sink, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 100000)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_summer_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("Sinking") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12)) 
# autumn
autumn_heatmap_surface <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_hex(data = total_autumn_surface, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 110000)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_autumn_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

autumn_heatmap_sink <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_hex(data = total_autumn_sink, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 110000)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_autumn_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

# winter
winter_heatmap_surface <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_hex(data = total_winter_surface, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 110000)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_winter_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

winter_heatmap_sink <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_hex(data = total_winter_sink, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 110000)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_winter_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

# spring
spring_heatmap_surface <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_hex(data = total_spring_surface, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 110000)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_spring_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

spring_heatmap_sink <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_hex(data = total_spring_sink, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 110000)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_spring_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12)) 
```

```{r message=FALSE, echo=FALSE, include=TRUE, warning=FALSE, fig.height=8, fig.width=6}

ggarrange(summer_heatmap_surface, summer_heatmap_sink, autumn_heatmap_surface, autumn_heatmap_sink, winter_heatmap_surface, winter_heatmap_sink, autumn_heatmap_surface, spring_heatmap_sink,common.legend = TRUE, font.label = list(size = 12, face = "bold"), legend = c("bottom"), ncol = 2, nrow = 4)

# Point plots
## Depth and surface distribution
```{r message=FALSE, echo=FALSE, warning=FALSE}
# summer
summer_depth_sink <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_point(data = total_summer_sink, aes(x = lon, y = lat, colour = KelpDepth)) +
  scale_colour_viridis_c(aesthetics = "colour", option = "C", limits = c(0, 1500)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_summer_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("Summer") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12)) 
# autumn
autumn_depth_sink <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_point(data = total_autumn_sink, aes(x = lon, y = lat, colour = KelpDepth)) +
  scale_colour_viridis_c(aesthetics = "colour", option = "C", limits = c(0, 1500)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_summer_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("Autumn") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))
# winter
winter_depth_sink <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_point(data = total_winter_sink, aes(x = lon, y = lat, colour = KelpDepth)) +
  scale_colour_viridis_c(aesthetics = "colour", option = "C", limits = c(0, 1500)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_summer_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("Winter") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12)) 
# spring
spring_depth_sink <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_point(data = total_spring_sink, aes(x = lon, y = lat, colour = KelpDepth)) +
  scale_colour_viridis_c(aesthetics = "colour", option = "C", limits = c(1, 500)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  #geom_path(data = total_summer_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("Spring") +
  guides(fill=guide_legend(title="Number of particles")) +
  #theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12)) 
```

```{r message=FALSE, echo=FALSE, warning=FALSE, include=TRUE}

ggarrange(summer_depth_sink, autumn_depth_sink, winter_depth_sink, spring_depth_sink,common.legend = TRUE, font.label = list(size = 12, face = "bold"), legend = c("bottom"), ncol = 2, nrow = 2)
